### 2015-06-04 LOI/inc2.tex

\underline{\textbf{Objectives:}} Exascale scientific discovery will
introduce more complex hardware, and many simulations will be bottlenecked 
without sufficient new research into manging and storing the large data which will be
produced during the simulation, and analzyed for months after the simulations.
Our goal is to explore and address
the multi-tier challenges that are faced by scientists in creating and
managing and storing their data  to expedite insights into
mission critical scientific processes in exascale computing.
%
We propose a research program that aims to explore a hiearchical organization and storage infstraturure which will facilitiate 
how we data can be written and read efficiently. In order to help us explore our many research issues, we will build upon the
sucess of our middleware system, ADIOS, our multi-tier storage system, Sirocco, and our distributed storage system, Cepth.
We will also take advantage of our staging system, Data Spaces, and our Comon communication Interface (CCI) and build on all of
our sucessful software used in petascale simulations to understand the new directions which need to be understood to fully develop
the next generation I/O and Storage System for exascale and beyond systems.

>>>>

\underline{\textbf{Objectives:}} Exascale scientific discovery will
introduce more complex hardware, and many simulations will be bottlenecked 
without sufficient new research into managing and storing the large data which will be
produced during the simulation, and analzyed for months after the simulations.
Our goal is to explore and address
the multi-tier challenges that are faced by scientists in creating and
managing and storing their data  to expedite insights xsinto
mission critical scientific processes in exascale compuxsting.
%
We propose a research program that aims to explore a hiearchical organization and storage infstraturure which will facilitiate 
how we data can be written and read efficiently. In order to help us explore our many research issues, we will build upon the
sucess of our middleware system, ADIOS, our multi-tier storage system, Sirocco, and our distributed storage system, Cepth.
We will also take advantage of our staging system, Data Spaces, and our Comon communication Interface (CCI) and build on all of
our sucessful software used in petascale simulations to understand the new directions which need to be understood to fully develop
the next generation I/O and Storage System for exascale and beyond systems.
